DeepSched: A Deep Representation Of Scheduling Policies For Heterogeneous Distributed Systems

### 2020-04-10 paper/core/exp_setup.tex
added evaluation and TA chart

\subsubsection{Genetic Algorithms}
The methodology from \cite{article2} is used to develop a genetic algorithm solution for heterogeneous systems. Extra parameters are added to the population to represent the different resources. Also, the execution time is expanded to be a value for each job running on a specific machine, instead of only one execution time value. The used fitness function is the average waiting time \ref{eq:ga}. Random initialization is used along with Crossover. The results of this method are compared to the output of the proposed network.

\subsection{Datasets}
A database of tasks and resources is adapted from \emph{Dataset for Task scheduling in Cloud using CLoudsim} \cite{px5b-b729-20}. The used database consists of $100000$ samples represented as a list of tasks requires to be scheduled. Each sample contains from $486$ to $84654$ tasks, arranged as a \emph{directed acyclic graph} (DAG) to represent the task dependencies and each task has an execution time for each specific processor. Also, the database contains $188$ resource instances (processors), on which the given tasks scheduled. The desired output of such data is to determine, for each task, the optimal processor to run on, the actual start time (AST) and the actual finish time (AFT).

@@

\subsection{Training}
The network is trained on HEFT scheduling outputs. Cross-entropy is used as a classification loss and mean squared error (MSE) is used as a regression loss. The summation of the two losses \ref{eq:l} is used to train the network using gradient descent with \emph{Adam} optimizer and a learning rate of $1e$-$5$. The network is trained for $100$ epochs. The training takes around $1.5$ hours on \emph{Nvidia GTX} $1070$ and around $13$ hours on \emph{Nvidia GTX} $840m$, which is a relatively small time based on both \emph{GPUs} performance.

\subsection{Inference}
Inference is performed on the trained network using both seen and unseen data, in order to compare with both HEFT and genetic algorithms, based on time and performance.

>>>>

\subsubsection{Genetic Algorithms}
The methodology from \cite{article2} is used to develop a genetic algorithm solution for heterogeneous systems. Extra parameters are added to the population to represent the different resources. Also, the execution time is expanded to be a value for each task running on a specific machine, instead of only one execution time value. The used fitness function is the average waiting time \ref{eq:ga}. Random initialization is used along with Crossover. The results of this method are compared to the output of the proposed network.

\subsection{Datasets}
A database of tasks and resources is adapted from \emph{Dataset for Task scheduling in Cloud using CLoudsim} \cite{px5b-b729-20}. The used database consists of $100000$ samples represented as a list of tasks requires to be scheduled. Each sample contains from $486$ to $84654$ tasks, arranged as a \emph{directed acyclic graph} (DAG) to represent the task dependencies and each task has an execution time for each specific processor. Also, the database contains $188$ resource instances (processors), on which the given tasks scheduled. The desired output of such data is to determine, for each task, the optimal processor to run on, the actual start time (AST) and the actual finish time (AFT). \\

@@

\subsection{Training}
The network is trained on HEFT scheduling outputs. Cross-entropy is used as a classification loss and mean squared error (MSE) is used as a regression loss. The summation of the two losses \ref{eq:l} is used to train the network using gradient descent with \emph{Adam} optimizer and a learning rate of $1e$-$5$. The network is trained for $100$ epochs. The task encoder only takes input of maximum number of tasks, so inputs of lower dimension are zero-padded along the length dimension to the maximum number ($84654$ tasks). \\

The training takes around $1.5$ hours on \emph{Nvidia GTX} $1070$ and around $15$ hours on \emph{Nvidia GTX} $840m$, which is a relatively small time based on both \emph{GPUs} performance.

\subsection{Inference}
Inference is performed on the trained network using both train and test data. We use the same $188$ resources information for all tests, however the input list of tasks is zero-padded to the maximum number of tasks, exactly like training.

\subsection{Evaluation}
The evaluation of our proposed method is conducted through running inference on both seen and unseen data of different lengths. These results of the network are compared to the output of HEFT and GA methods in the same scenarios.

This is done by passing the schedule produced by the three methods through a simple simulation that runs the proposed schedule and calculates the average turnaround time of all tasks. Evaluation is also conducted on the execution time of each scheduling method, as the speed of the scheduling algorithm is one of our main targets.
